### 2019-01-02 Sections/authors.tex
tiny
Economics essay
Minor, superdense coding, authors
Touch up
Fixed up telescopy
Touch ups
Added atul
Minor edits from Chandra
Dist quantum search update
Added game theory section

\boldauthor{Peter P. Rohde}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\smallaffiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\boldauthor{He-Liang Huang}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}
\smallaffiliation{Henan Key Laboratory of Quantum Information \& Cryptography, Zhengzhou Information Science and Technology Institute, Zhengzhou, Henan 450000, China}

@@

\boldauthor{Zu-En Su}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}

\boldauthor{Zixin Huang}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield}

%
% Chris Ferrie
%

\boldauthor{Chris Ferrie}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\boldauthor{Simon Devitt}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\boldauthor{Rohit Ramakrishnan}
\smallaffiliation{Indian Institute of Science, Bangalore, India}

@@

\boldauthor{Si-Hui Tan}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

@@

\boldauthor{Nana Liu}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

%
% Ryan L. Mann
%

\boldauthor{Ryan L. Mann}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

%
% Samuel I. Marks
%

%\boldauthor{Samuel I. Marks}
%\smallaffiliation{University of Sydney, Australia}

@@

\boldauthor{Jonathan P. Dowling}
\smallaffiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\boldauthor{Tim Byrnes}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\smallaffiliation{Department of Physics, New York University, New York, NY 10003, USA}

@@

\boldauthor{William J. Munro}
\smallaffiliation{NTT Basic Research Laboratories, 3-1 Morinosato-Wakamiya, Atsugi, Kanagawa 243-0198, Japan}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}

%
% Chao-Yang Lu
%

%\boldauthor{Chao-Yang Lu}
%\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
%\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
%\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}

%
% Christopher Altman
%

%\boldauthor{Christopher Altman}
%\smallaffiliation{???}

>>>>

\boldauthor{Peter P. Rohde {\normalfont(ed.)}}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\smallaffiliation{Hearne Institute for Theoretical Physics, Louisiana State University, Baton Rouge, LA 70803, United States}

\boldauthor{Zixin Huang}
%\email{zixin.huang@sheffield.ac.uk}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield}

@@

\boldauthor{He-Liang Huang}
%\email{quanhhl@mail.ustc.edu.cn}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}
\smallaffiliation{Henan Key Laboratory of Quantum Information \& Cryptography, Zhengzhou Information Science and Technology Institute, Zhengzhou, Henan 450000, China}

@@

\boldauthor{Zu-En Su}
%\email{zuensu@gmail.com}
\smallaffiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\smallaffiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}

@@

\boldauthor{Simon Devitt}
%\email{simon.devitt@uts.edu.au}
\smallaffiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

@@

\boldauthor{Rohit Ramakrishnan}
%\email{rohit.k.ramakrishnan@gmail.com}
\smallaffiliation{Indian Institute of Science, Bangalore, India}

%
% Atul Mantri
%

\boldauthor{Atul Mantri}
%\email{atul\_mantri@mymail.sutd.edu.sg}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}
\smallaffiliation{Centre for Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543}

@@

\boldauthor{Si-Hui Tan}
%\email{sihui.tan@gmail.com}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

@@

\boldauthor{Nana Liu}
%\email{coronocephalus@gmail.com}
\smallaffiliation{Singapore University of Technology \& Design, 20 Dover Dr, Singapore 138682}

%
% Scott Harrison
%

\boldauthor{Scott Harrison}
%\email{harrison@dipf.de}
\smallaffiliation{Leibniz Institute for Research \& Information in Education, Rostocker Stra{\ss}e 6, 60323 Frankfurt am Main, Germany}

%
% Darryl Vietch
%

\boldauthor{Darryl Vietch}
%\email{darryl.veitch@uts.edu.au}
\smallaffiliation{University of Technology Sydney, NSW 2007, Australia}

%
% Chandrashekar Radhakrishnan
%

\boldauthor{Chandrashekar Radhakrishnan}
%\email{chandrashekar10@gmail.com}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China}

@@

\boldauthor{Jonathan P. Dowling}
%\email{jdowling@lsu.edu}
\smallaffiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

@@

\boldauthor{Tim Byrnes}
%\email{tim.byrnes@nyu.edu}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\smallaffiliation{Department of Physics, New York University, New York, NY 10003, USA}

@@

\boldauthor{William J. Munro}
%\email{bill.munro@me.com}
\smallaffiliation{NTT Basic Research Laboratories, 3-1 Morinosato-Wakamiya, Atsugi, Kanagawa 243-0198, Japan}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}

### 2019-01-02 Sections/economics_of_the_quantum_internet.tex
Added authors to sections
indexing
Added game theory section

\section{Economic properties of the qubit marketplace}\index{Economic properties}\label{sec:econ_prop}

@@

@@

\subsection{Game theory of the qubit}\index{Game theory}\label{sec:game_theory}

Previously we discussed the implications of the imposition of taxation on the qubit market, assuming it operates in a relatively competitive environment. However, given the massive technological and financial investment made to realise just a single quantum computing system, let alone an entire network, the likely resulting market structure will not be a perfectly competitive one. Rather, just a few significant firms will likely dominate the space, creating a global oligopoly where profit extraction in the face of various taxation frameworks is to be the more likely scenario.

This then leads to game theory, which can make a significant contribution to our understanding of how a potential qubit market is not only likely to operate, but more importantly, that the suppliers of qubits will be engaging in a cooperative game with each other to maximise their utility (profits), while governments will be engaging in a competitive game with other governments with a clear objective: maximise taxation revenue, while not ceding ground to competing countries in hosting qubits. The following sections will discuss these games and provide an indication of how various strategies perform in terms of cooperation and competition.

\subsubsection{The Nash equilibrium \& VNM solution for maximal utility}\index{Nash equilibrium}

\comment{To do}

>>>>

\section{Economic properties of the qubit marketplace}\index{Economics!Properties}\label{sec:econ_prop}

\sectionby{Scott Harrison}

@@

\sectionby{Scott Harrison}

@@

\subsection{Game theory of the qubit marketplace}\index{Game theory}\label{sec:game_theory}

\sectionby{Scott Harrison}

\startnormtable

In this part, it was established how a qubit market can function, and how the pricing mechanisms of various derivatives may work. One of the more interesting dimensions to the development of the quantum internet, is understanding \textit{how} the cooperation\index{Cooperation} between different suppliers will occur. Importantly, the cost of building quantum computers means that there may be a limited number of competing vendors -- for profit maximisation to occur, the most likely outcome is cooperation between them. The main question is, what can be learnt from applying game theoretic techniques to the strategies available to quantum computing vendors? Importantly, what are the implications associated with supply-side shifts, such as the imposition of taxation\index{Taxation}.

To analyse the decision making options for qubit suppliers, game theory is an analytical tool to understand `games', where the outcome of the game is dependent on the various strategies employed by agents within it. The most well-known of these games is the prisoner's dilemma\index{Prisoner's dilemma} \cite{(Flood and Dresher, 1950)}\comment{Please provide refs.}, describing the potential risks and rewards for two prisoners who are being questioned about a crime. This type of game is typically called a \textit{two-person, non-zero sum, non-cooperative game}\index{Two-person, non-zero sum, non-cooperative games} \cite{bib:Bacharach76}. More detailed examples of game theory have explored many of the base assumptions of this scenario, such as what if the prisoners are able to cooperate from the outset? How does this then result in maximising utility, and is cooperation always the best answer?

In the case of the quantum internet, it should be clear from the outset that there is a strong benefit associated with cooperation between vendors. Cooperative games form an important subset of the game theory domain, and are the most applicable to quantum computing. As indicated previously, there will be exponential increases in computing power from integrating quantum computing systems, and as such, any qubit supplier will ultimately be able to produce excess computational power through linking and cooperating with other systems via the computational leverage phenomenon (Sec.~\ref{sec:comp_lev}). This idea is at the centre of the analysis when applying game theory to the decision making of suppliers.

For the uninitiated to economic analysis, particularly game theory, a few key concepts need to be established. This chapter by no means tries to cover these concepts in complete detail. For more detailed information we suggest referring to \cite{???}\comment{Please provide refs.}. Furthermore, the analysis at this point is only descriptive in nature, as a means of establishing the space where new research can be developed. More rigorous investigation is encouraged.

The first concept is the idea of \textit{utility}\index{Utility}, which can be generally defined as `the ability to assign a number (utility) to each alternative so that, for any two alternatives, one is preferred to the other if and only if the utility of the first is greater than the utility of the second' \cite{bib:Fishburn70}. In this regard, utility is often seen as a representation of the overall benefit associated with a decision or preference. As utility is unobservable, it can become subjective in nature. However, the key is not whether the values assigned to any one preference are subjective, but rather whether the assigned values associated with competing decisions are comparable, so that they can be quantitatively ranked. Thus, utility is a tool for comparison.

The second concept is the \textit{utility payoff matrix}\index{Utility!Payoff matrices}. Utility values assigned to any possible decision can be formulated into a matrix, which collates all the possible decisions from a given decision maker's perspective. In a game with two participants, this would result in a 2-dimensional matrix. With $n$ decision makers, there would have an $n$-dimensional matrix representation. The matrix also forms the basis of the graphical analysis undertaken throughout this chapter for the 2-dimensional cases.

The third concept is the \textit{negotiation set}\index{Negotiation sets}, which defines a space of possible preferences. The negotiation set was first introduced in the seminal work of \cite{bib:NeumanMorgenstern44}. At its most basic, the negotiation set forms a set of bounds for the payoff matrix. This limits possible solutions for a game to strategies that would actually see an improvement in the individual's utility above the base alternative of making no decision at all. This is also referred to as the \textit{status quo}\index{Status quo}.

To best develop an understanding of how a quantum internet game will be played out, we will begin by analysing the utility payoff space for classical computing. Currently we can easily define three key strategies for two firms ($X$ and $Y$), needing access to conventional computing resources. The first strategy is that $X$ and $Y$ build their own systems in isolation, and there is no cooperation or networking of computational resources between them. This can be considered the status quo ($S$) for the firms, as it represents the autarky position and defines the von Neuman \& Morgenstern utility space\index{Utility!Space}.  This is represented in Fig.~\ref{fig:game_theory_1}, where the bold dashed lines show the minimum utility payoff for $X$ and $Y$. Importantly, any changes to $X$'s computational capacity has no impact on $Y$. So $X$ can take any position along the horizontal axis, and there is no change in $Y$'s utility, and vice versa. The resulting utility point, however, is described here as the intersecting minimum of these options, represented by the point \mbox{$(S_x, S_y)$}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_1}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_1}
\end{figure}

The second strategy is that either $X$ or $Y$ builds their own system, but then licences unused compute-cycles to the other. This means that the other player may still be able to do the necessary computations, but essentially outsources the setup costs and ongoing maintenance of computing infrastructure. This also in turn will improve the utilisation of the system for the player who builds the system, resulting in increased efficiency, profitability and subsequently utility (under the conditions of increasing economies of scale and assuming homogenous system requirements).

The final strategy available to the firms is to consolidate their resources into a distributed cloud computing environment (Sec.~\ref{sec:dist_comp}), where the limitations of a single system are lifted, allowing for even better resource-sharing and improvement beyond what a single system solution can offer. In this scenario, both providers will be able to collaborate such that they can meet their individual computational requirements, without having to fully build independent systems like that in the licensing strategy. Importantly though, while there may be a small loss in utility for one of the parties compared to the licensing strategy, the cooperation allows an overall higher level of utility to be achieved jointly, creating a Nash equilibrium\index{Nash equilibrium} at this point, $C$.

This can be described in the utility payoff matrix outlined in Tab.~\ref{tab:game_theory_1}, where `$\leftarrow/\rightarrow$' indicates the licensing (from/to) strategy, `+' indicates the cloud computing cooperation strategy, and the off-diagonal combinations are the status quo, indicating no cooperation.

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(2.5,2.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_1}
\end{table}

It's important to note that these values are totally arbitrary in nature, and do not have a `real life' interpretation, other than understanding the preferencing of the described strategies. For initial simplicity, the matrix assumes that $A$ and $B$ derive identical utility values from the strategies, resulting in a symmetrical representation of the choices in Fig.~\ref{fig:game_theory_2} around the diagonal axis.

Translating the utility payoff matrix into a graphical representation yields Fig.~\ref{fig:game_theory_2}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_2}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_2}
\end{figure}

As indicated previously, the bold dashed lines parallel to the axes indicate the status quo of no cooperation between $X$ and $Y$. Point $A$ indicates the utility combination where $X$ builds the system and licenses out time to $Y$, and $B$ represents the reverse. $C$ is the point where both $X$ and $Y$ cooperate through distributed cloud computing, maximising the overall utility for both players. Important to note is that there is some loss of utility for both individual players, relative to having built the systems and licensed the resources out. This assumes that there is some inefficiency through transaction costs associated with establishing the collaboration, along with the need to balance the other player's requirements for compute-time. However, point $C$ is also the Nash equilibrium\index{Nash equilibrium}, where cooperative bargaining would result in the best outcome overall. The lines connecting $A$ to $C$, and $B$ to $C$, indicate possible solutions where mixed strategies\index{Mixed strategies} of licensing time and cloud computing can be found\footnote{This is an over-simplified example of the classical computing environment and is only meant to serve as a means of establishing the basic concepts for comparison.}.

Now, quantum computing uses similar strategies for possible solutions, with one key difference. Using classical computing, the relationship for the cloud strategy was described as additive in nature, where the computational resources of both players are accumulated additively when unified into a larger virtual quantum computer. In the quantum cloud computing strategy, this effect is enhanced by their super-linear linear computational leverage. For the sake of illustration, we will now assume this becomes multiplicative\footnote{In practise, a complete formalism would be expressed in terms of computational scaling functions, $f_\mathrm{sc}$ (Sec.~\ref{sec:comp_sc_func}).}. As such, should $X$ and $Y$ build identical quantum computers, the hypothesised payoff matrix would become as shown in Tab.~\ref{tab:game_theory_2}.

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(5,5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_2}
\end{table}

In this scenario, the status quo utility for building quantum systems with no collaboration, and the licensing strategy are assumed to yield the same utility payoffs as in the classical computing scenario. This means that the only difference in the matrix payoff arises when $X$ and $Y$ collaborate over the quantum cloud. The resulting graphical representation of this payoff matrix is shown in Fig.~\ref{fig:game_theory_3}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_3}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_3}
\end{figure}

Moving to the quantum computing scenario, point $Q$ now represents the collaborative point, where there is a multiplicative increase in the utility payoff for $X$ and $Y$. This captures the benefits of increased computational power through the quantum internet, which is not possible through classical computing at point $C$. Furthermore, any mixed strategy\index{Mixed strategy} of licensing and cloud computing will result in a non-linear transition from points $A$ or $B$ to $Q$. Finally, $Q$ will still be subject to other economic forces, like diminishing marginal returns, constraining it to a real solution. That is, there is no infinite gain in utility as a result of cooperation. This now establishes both the key differences between classical and quantum computing utility payoff spaces, and underscores two main questions that are explored in more detail using this framework.

The first question is how do mixed strategies\index{Mixed strategies} affect cooperation? To perform this analysis, assume that $X$ has chosen a mixed strategy with a combination of licensing and cloud computing. As illustrated in Fig.~\ref{fig:game_theory_4}, this results in a utility value of 4, represented by the vertical dotted line.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_4}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_4}
\end{figure}

By extension, this results in two possible solutions, $X'$ and $X''$, that intersect the lines $AQ$ and $BQ$ respectively. $X'$ represents a point where more compute-time is allocated to a licensing strategy, and less to cloud computing, while $X''$ is the converse. $X$ is indifferent to both solutions, as they result in the same utility, but for $Y$, there is a clear choice. $X''$ will result in higher utility, placing an emphasis on cooperation. Once $Y$ has chosen their strategy, this then means that $X$ can revise their original choice too. The consequence is a progressive march towards the overall optimal solution $Q$, as shown in Fig.~\ref{fig:game_theory_5}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_5}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_5}
\end{figure}

The conclusion from this is that while mixed strategies\index{Mixed strategies} of licensing and cloud computing will be possible in a quantum internet, there will always be an underlying pressure on players to cooperate.

The second question that arises is what happens to the utility payoff matrix when taxation is imposed?\index{Taxation} The assumption that $X$ and $Y$ are operating in similar regulatory environments can be relaxed. As identified in Sec.~\ref{XX}, the imposition of a tax on quantum computing is highly likely given its inelastic nature as a commodity. As such, the question becomes, what happens when $X$ is in a more heavily taxed environment, or something impacts the utility achieved by the players asymmetrically. Economically, a tax operates by transferring utility from the supplier of a good to the government. As shown in the market analysis, this will result in a small reduction in supply, but overall it should remain at a similar level. However, in the cloud computing strategy, even small reductions in supply are exponentially multiplied. The result is that all collaborative strategies will yield less utility for $X$, as it both reduces supply and transfers utility to government. The impact however is also felt by $Y$, as the overall computational power of the cloud is reduced in the cloud computing strategy. This results in a payoff matrix as shown in Tab.~\ref{tab:game_theory_3}.

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(2,1.25)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(3,4.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_3}
\end{table}

For the strategy where $X$ licenses compute-time to $Y$, there has been a reduction in utility derived by $X$. The small reduction in supply will also mean that there is a reduction in the available compute-time available to be licensed to $Y$. For the licensing strategy, this means there would be a shift in utility from $(3,1.5)$ in Tab.~\ref{tab:game_theory_2} to $(2, 1.25)$ in Tab.~\ref{tab:game_theory_3}. Graphically, this is shown as the inward shift from point $A$ to $A'$ in Fig.~\ref{fig:game_theory_4}. We also assume here that the imposition of the tax itself doesn't completely abolish any utility gains from the licensing strategy over the status quo.

For the cloud computing strategy, there will be multiplicative decreases in the final utility payoff. As such, the utility payoff shows a new combination of $(3,4.5)$, an asymmetric reduction from the previous position of $(5,5)$. Graphically, this is shown in Fig.~\ref{fig:game_theory_6} as a shift from $Q$ to $Q'$.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_6}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_6}
\end{figure}

Two things can be made clear from both the matrix and resulting graphical representation. The imposition of taxation affects both the licensing and cloud computing strategies, but unequally. For $X$, the imposition of taxation results in a greater loss in net utility in the cloud computing strategy. This would ultimately affect the likelihood for $X$ to choose this strategy. Secondly, the rate at which utility is gained through a mixed strategy\index{Mixed strategies} (moving from $A'$ to $Q'$) has decreased. This implies that, in a cooperative game, $X$ would be less motivated to cooperate with $Y$ than $Y$ would be to cooperate with $X$. Point $Q'$ would still lead to the maximum utility payoff, but the negotiation process to achieve it will be more difficult owing to the utility asymmetry. Thus, despite both players having identical systems, the regulatory environment will strongly impact the likelihood of cooperation. This has important implications for future policy-making.

This raises the next assumption, what happens with collaboration between firms who have different systems? If this assumption is relaxed, what comes of the resulting utility payoff matrix and choice of strategies? The analysis for this assumption had already been presented in the previous discussion. The effective impact of taxation is that it will limit the amount of computational power delivered to market and capture governmental revenue from the sale of compute-time. This is analogous to what happens if $X$ was to build a less powerful system than $Y$. Through collaboration, they could still attain point $Q'$, shown in Fig.~\ref{fig:game_theory_4}, but this time the asymmetrical arises as a consequence of system design. Despite $X$ now not contributing as much to the overall computational power of the quantum cloud, choosing the maximising strategy of offering all available computing power to a cloud configuration, does maximise individual utility. Furthermore, the subjective nature of the utility derivation means there doesn't have to be a change from the described payoff matrix shown in Fig.~\ref{fig:game_theory_3}. Despite having a less powerful system, the proportional allocation of financial rewards relative to the contribution, means both $X$ and $Y$ could maintain a symmetric utility payoff outcome, like in Fig.~\ref{fig:game_theory_3}. What can be concluded from this analysis is that in a 2-player cooperative game, the player with the more powerful system also has a greater incentive to cooperate\comment{Contradicts earlier conclusion. In my earlier derivations I argued that the leverage phenomena incentivises smaller players more than bigger ones since their leverage is greater. Please clarify or reconcile.}.

This then leads to one final question, `What happens when the analysis moves beyond just two players?' As established previously, the cost and scale limitations associated with quantum computing means there are likely to be limited suppliers contributing to the quantum internet. However, it's also likely that there will be more than just two. Formulating the $n$-person cooperative game opens up a plethora of possibilities that go beyond the scope of this introductory discussion, but one key take away point from the previous analysis is that there is a strong motivation for cooperation. This then introduces two possible scenarios:

\begin{itemize}
	\item There is complete cooperation between all suppliers.
	\item Competing cartels develop, where for external reasons (e.g. political, geographical, ideological, strategic), there is a benefit in cooperating with just a few players, and acting as a single supplier in direct competition with other cartels.
\end{itemize}

The first scenario is by far the most attractive, and in a world where free negotiations may take place, this is clearly the option resulting in both attaining the greatest computational power for the quantum internet, and also the greatest utility maximisation for all participants involved. The end result will be similar to that shown in Fig.~\ref{fig:game_theory_3}. This implies that the quantum internet market structure would become like a natural monopoly, with diminishing long-run average costs as supply is increased. It would also mean that there is a strong case for some government involvement to prevent profit maximisation at the expense of efficiency.

However, history has shown us that another plausible outcome is the second scenario. While there are motivations to collaborate, there are also motivations to compete. Given the almost certain involvement of government intervention in the supply of quantum processing, the formulation of regional cartels due to external factors may also be a likely outcome. In such an environment, the cartels will internally operate like $n$-player cooperative games, but externally towards other conglomerates, operate like $n$-player competitive games \cite{bib:Bacharach76}. This result may still result in Pareto optimal and efficient outcomes at a market level, but will always fall short relative to a complete cooperation model. This scenario will then end with an oligopolistic market structure.

In summary, a game theory approach to understanding the quantum internet shows that there are strong motivations to cooperate between qubit vendors to maximise utility. Furthermore, there is a strong potential to affect the possibility of cooperation through market distorting effects like the imposition of taxation. Finally, the two most likely market structures that will develop under the quantum internet are either a natural monopoly, where some form of regulation will be required to ensure economically efficient production, or an oligopoly, where a few cartels will compete with each other to maximise their productive output. Either way, the quantum internet marketplace will be an interesting source of future research potential when it becomes a reality.
